Development of outdoor air pollution models for estimating exposure in the Barcelona Life Study Cohort (BiSC)

### 2023-11-10 manuscript_BiSC.tex
Updates from Overleaf

Urban areas add a layer of complexity to air pollution modelling due to complex spatiotemporal patternts that difficult accurate estimation of ground-level air pollutant concentrations \cite{sokhi2022}. In response to these challenges, machine learning (ML) algorithms have been increasingly used, particularly decision trees based models \cite{liu2022}. These family of models, are often used due to their ability to model non-linear and potential interaction among predictive variables \cite{liu2022treebased}. Among the different ML algorithm, random forest (RF) has emerged as one of the most robust techniques for predicting outdoor air pollution concentrations \cite{chen2019, chen2020, stafoggia2019, stafoggia2020, schneider2020, mila2023}.

@@

Air pollution measurements were conducted during two separated monitoring campaigns. The first campaign was carried out in accordance with the ESCAPE guidelines. This included four distinct measurements periods: three in the winter, summer, and autumn of 2021, and a final one in the winter of 2022. During these periods, levels of NO\textsubscript{2}, PM\textsubscript{2.5}, and BC were measured at 34 locations across Barcelona Metropolitan Area (Barcelona, Esplugues de Llobregat, and L'Hospitalet). This monitoring campaign was named "BiSCAPE" campaign. The second monitoring campaign was conducted at homes of the BiSC participants, one week during the first trimester and one week during the third trimester of pregnancy, during the period 2018-2021, and only NO\textsubscript{2} levels were measured. This monitoring campaign was named "BiSC-home" campaign. These monitoring campaigns where used in the development of the LUR and hybrid models.

>>>>

Urban areas add a layer of complexity to air pollution modelling due to complex spatiotemporal patterns that difficult accurate estimation of ground-level air pollutant concentrations \cite{sokhi2022}. In response to these challenges, machine learning (ML) algorithms have been increasingly used, particularly decision trees based models \cite{liu2022}. This family of models is often used due to its ability to model potential, nonlinear interaction between predictor variables \cite{liu2022treebased}. Among the different ML algorithm, random forest (RF) has emerged as one of the most robust techniques for predicting outdoor air pollution concentrations \cite{chen2019, chen2020, stafoggia2019, stafoggia2020, schneider2020, mila2023}.

@@

Air pollution measurements were conducted during two separate monitoring campaigns. The first, named the "BiSC-home" campaign, took place at the home addresses of BiSC participants and involved measuring only NO\textsubscript{2} levels for one week during the first, and third trimester of pregnancy between 2018-2021. The second campaign was carried out in accordance to the ESCAPE guidelines, named "BiSCAPE", included four distinct measurements periods: three in the winter, summer, and autumn of 2021, and a final one in the winter of 2022. During these periods, levels of NO\textsubscript{2}, PM\textsubscript{2.5}, and BC were measured at 34 locations across Barcelona Metropolitan Area (Barcelona, Esplugues de Llobregat, and L'Hospitalet).These monitoring campaigns where used in the development of the LUR and hybrid models.
